### 2015-02-02 src/2_Finance.tex
Finance chapter ready

In order to determine the execution price, buyers and sellers orders are placed
in an order book which help to determine which order can be fulfilled.
Figure~\ref{fig:orderbook} illustrates how buyers and sellers are ordered. The
ask or offer price is the current lower price a seller is willing to accept for
a good. The bid price corresponds to the current highest price a buyer is
willing to pay for a good. Orders with the same price are prioritized by
arrival time and placed on top of the book.  The difference between current ask and bid
price is called spread and their average is called mid-price.

@@

\section{Technical analysis}

\section{Fundamental analysis}

@@

The weak form claims that prices already reflect all past publicly available information. Then strategies based on technical analysis will not be able to produce excess returns. However, the weak form accepts that some forms of fundamental analysis may still provide excess return. Therefore, future prices cannot be predicted based on analysis of historical data. This implies that future prices movements are determined entirely by information not contained in the past prices and participants are unable to systematically profit from market inefficiencies. 
However, many studies have shown a marked tendency for the stock markets to trend over time periods. Various explanations for such large and apparently non-random price movements have been promulgated. Even Fama has accepted price anomalies which do not follow the weak-form efficiency hypothesis \cite{fama+french2008}.

The semi-strong form of the EMH claims that prices instantly change to reflect new public (not private) information such that no excess return can be obtained. In this form neither technical or fundamental analysis can produce excess return.

@@

>>>>

In order to determine the execution price, buyers and sellers orders are placed
in an order book which help to determine which order can be fulfilled.
Figure~\ref{fig:orderbook} illustrates how buyers and sellers are ordered. The
ask or offer price is the current lower price a seller is willing to accept for
a good. The bid price corresponds to the current highest price a buyer is
willing to pay for a good. Orders with the same price are prioritised by
arrival time and placed on top of the book.  The difference between current ask and bid
price is called spread and their average is called mid-price.

@@

@@

The weak form claims that prices already reflect all past publicly available information. Therefore, future prices cannot be predicted based on analysis of historical data. This implies that future prices movements are determined entirely by information not contained in the past prices and participants are unable to systematically profit from market inefficiencies. 
However, many studies have shown a marked tendency for the stock markets to trend over time periods. Various explanations for such large and apparently non-random price movements have been promulgated. Even Fama has accepted price anomalies which do not follow the weak-form efficiency hypothesis \cite{fama+french2008}.

The semi-strong form of the EMH claims that prices instantly change to reflect new public (not private) information such that no excess return can be obtained.

@@

EMH is related with two approaches to investment analysis: fundamental and technical analysis. Fundamental analysts base their predictions of stock price behaviour on fundamental factors such as internal information of a company, its industry or the economy. Technical analysts, by contrast, consider that all this financial information is already included in the prices and believe that future stock prices can be predicted studying the historical market behaviour. A market technician bases its predictions on historical patterns of prices of volume changes.

Under the weak form of EMH, strategies based on technical analysis will not be able to produce excess returns. However, the weak form accepts that some forms of fundamental analysis may still provide excess return. Similarly, the semi-strong form of EMH  neither technical or fundamental analysis can produce excess return.

If the stock market efficiently digests all available information, there is little justification for seeking excess returns gains from investing. However, EMH doesn't lessen the the importance of investing only change its philosophy. The only way an investor can possibly obtain higher returns is by purchasing riskier investments.

 Researches can determine now how efficient a financial market is, i.e how efficiently information is processed.
